A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-14 paper.tex
Remove author information
Be anonymous for reviewing.
Reoganize experiment and move time complexity

The E2EE protocol framework presented in this paper combines a series of different cryptographic procedures. Each of them can be chosen on the basis of the working hardware and scenario by developers. On some certain devices, hardware acceleration would be supported. With hardware acceleration, the elapsed time could be dropped a step more. For example applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration}

\subsubsection{Time Complexity}
In this paper, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and ECDSA P-256 for digital signature. In this E2EE protocol, ECDSA would take constant time, since the string needed to be signed is in fixed length. HMAC and AES-CBC are the procedures that cost most of the elapsed time. Time complexity of HMAC with SHA-256 is $O(n)$.\cite{hmac_time_complexity} Block cipher takes constant time for a single block which cause the time complexity is $O(n)$, too. Therefore, the E2EE protocol framework takes only linear time versus arbitrary string length.

@@

\subsubsection{Experiment}
Applying remote PoW greatly reduce the elapsed time. Channel creation is the next primary barrier for low-level devices to broadcast MAM message. With employing delegated MAM and E2EE, MAM channel creation would be delegated by tangle-accelerator which dramatically enhances the efficiency and makes MAM available for low-level devices. What follows is the performance comparison between MAM and delegated MAM for different payload sizes. Elapsed time for internet communication and PoW are not included, because the processes after sending message to tangle-accelerator are the common steps. Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly. In addition, MAM Channel creation and E2EE asymmetric key pair generation are not included, too, because the two operations would seldom be executed. In the E2EE protocol framework, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and Curve P-256 for ECDSA, respectively.

>>>>

The E2EE protocol presented in this paper combines a series of different cryptographic procedures. Each of them can be chosen on the basis of the working hardware and scenario by developers. On some certain devices, hardware acceleration would be supported. With hardware acceleration, the elapsed time could be dropped a step more. For example applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration}

\subsubsection{Time Complexity}
In this paper, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and ECDSA P-256 for digital signature. In this E2EE protocol, ECDSA would take constant time, since the string needed to be signed is in fixed length. HMAC and AES-CBC are the procedures that cost most of the elapsed time. Time complexity of HMAC with SHA-256 is $O(n)$.\cite{hmac_time_complexity} Block cipher takes constant time for a single block which cause the time complexity is $O(n)$, too. Therefore, the E2EE protocol takes only linear time versus arbitrary string length.

@@

\subsubsection{Experiment}
Applying remote PoW greatly reduces the elapsed time. Channel creation is the next primary barrier for low-level devices to broadcast MAM messages. With employing delegated MAM and E2EE, MAM channel creation would be delegated to Tangle-accelerator which dramatically enhances the efficiency and makes MAM available for low-level devices. What follows is the performance comparison between MAM and delegated MAM for different payload sizes. Elapsed time for internet communication and PoW are not included, because the processes after sending messages to Tangle-accelerator are the common steps. Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly. In addition, MAM channel creation and E2EE asymmetric key pair generation are not included, too, because the two operations would seldom be executed. In the E2EE protocol, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and Curve P-256 for ECDSA, respectively.
